%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}



\cvname{Jérémie \newline MÉRIGEAULT} % Your name
\cvjobtitle{Big-Data \& Machine \\Learning Engineer, \\ Techlead Data Scientist} % Job title/career

\cvlinkedin{}
\cvnumberphone{+33 6 18 77 49 91} % Phone number
\cvsite{http://github.com/\textasciitilde JeremM} % Personal website
\cvmail{jeremie.merigeault@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar



%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions

	\twentyitem
    	{Apr 2021 - \\ Today}
        {Digital Factory}
        {\href{http://www.enedis.fr/}{Enedis}}
        {Technical Lead Data-Scientist.}
        {
        {\begin{itemize}

        \item Business Owner of Enedis Data Science on prem \& cloud platform.
        \item Trainer for multiple data training session : data-science, big-data infrastructure, dev-ops \& tools (MLFlow, Airflow).
        \item Development of shared API : data access, statistical tools.

    \end{itemize}}
        }

	\twentyitem
    	{Aug 2017 - \\Apr 2021}
        {Data Analitycs for Distribution (DAD) project}
        {\href{http://www.enedis.fr/}{Enedis}}
        {Technical Lead, Craftman \& Data-Scientist. Apache spark lover.}
        {
        {\begin{itemize}
        \item Machine learning (spark on hadoop \& HPC) for predictive maintenance (on french electricity distribution assets).
        \item Distributed graph computing on spark, geospatial data analysis.

    \end{itemize}}
        }

\twentyitem
    	{Feb 2013 - \\Aug 2017}
        {STM project, (Massive Treatment System) \& Datalabs}
        {\href{http://www.enedis.fr/}{Enedis}}
        {Developer \& Data-Scientist on Enedis Big-Data project.}
        {
        {\begin{itemize}
        \item Multiple Data Science projects : Human Resources, Metering, Network maintenance.
        \item Implementation of performance SLA et performance workflow. Benchmarks with Apache JMeter.
        \item Architecture design of Enedis new Big-Data architecture : Kafka, spark on hadoop.
    \end{itemize}}
        }

    \twentyitem
   	{Feb 2010 - \\ Jan 2013}
        {SIMM Project (Mass Market Information System)}
        {\href{http://www.edf.fr/}{EDF}}
        {Performance and Oracle expertise on EDF critical business software (CRM, billing \& BI) with huge amount of data (40TB).}
        {
        {\begin{itemize}
        \item Database evolutions design and implementation : Oracle 11g, data compression, partitioning, RAC Clustering. Database optimisation and SQL tuning with big data volumes.
        \item Management of Oracle experts team. Oracle contracts (support and consulting) follow-up.
    \end{itemize}}
        }


	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem
    	{2018 - 2019}
        {MSc part-time student}
        {\href{http://www.datasciencetech.institute/}{Data Science Tech Institute, Paris, France}}
        {}
        {Applied MSc in Data Science \& Artificial Intelligence}
	%\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}

\begin{twenty} % Environment for a list with descriptions
        \twentyitem
        {2007 - 2010}
        {Engineering student}
        {\href{http://www.insa-rouen.fr/}{INSA de Rouen, France}}
        {}
        {Information Systems Architecture}
        %\twentyitem{<dates>}{<title>}{<organization>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 PAPERS
%----------------------------------------------------------------------------------------
\section{Conference Papers}


\begin{itemize}

        \item \textit{"Predictive maintenance on overhead medium voltage network using transient faults data"} - CIRED 2023
        \item \textit{"Big data applications for improving the reliability of the french electricity distribution grid"} - Handbook of Smart Energy Systems, 2022 - Springer
        \item \textit{"Analysing overhead medium voltage network criticity with ai"} - CIRED 2021
        \item \textit{"Optimizing Replacement of Power Distribution Network Cables with Graph Computing and Machine Learning"} - ESREL 2020
        \item \textit{"Using Big Data analytics to improve flood resilience of the distribution grid" \& "Optimizing network replacement with AI"} - CIRED 2019
\end{itemize}

%
\end{document} 
